dendro

### 2017-05-26 analysis/analysis_chronologies.Rmd
change name

```{r, warning=FALSE, message=FALSE}
library("tidyverse")
library("stringr")
library("dplR")
library("knitr")
# library("detrendeR")
library("pander")
source(paste0(getwd(), '/script/R/bai_piovesan.R'))
source(paste0(getwd(), '/script/R/rw_byTree.R'))
```

@@

# Compute chronologies of BAI

### Compute Chrono

b <- bai_sj

chrono_bai <- function(bai_object){ 
  require(dplyr)

  b <- bai_object 
  # alpha <- as.numeric(alpha)

  # Prepare data 
  b_aux <- b %>% 
  ##  Create a variable of year 
  mutate(year = as.numeric(rownames(.))) %>% 
  ## melt data 
  gather(series, bai, -year) %>% 
  # remove NA values 
  filter(bai != "")

  # Compute mean, sd, se and sample deepth (n_trees)
  out <- b_aux %>% 
  group_by(year) %>% 
  summarise(bai_mean = mean(bai), 
            bai_sd = sd(bai), 
            bai_se = bai_sd / sqrt(n()), 
            n_trees = n()) %>% 
  as.data.frame()

  # Loess 
  l <- loess(b_aux$bai ~ b_aux$year, span = alpha)
  years_v <- seq(min(b_aux$year), max(b_aux$year), 1)

cro_sj <- chrono_bai(bai_sj)
cro_sj$level <- 'SJ'
cro_ca <- chrono_bai(bai_ca)
cro_ca$level <- 'CA'

# San JUan 
cro_sjH <- chrono_bai(bai_sjH)
cro_sjH$site <- 'SJ_High'

@@

cro %>% ggplot(aes(x=year, y=bai_mean/100, colour=site)) + 
  theme_bw() + ylab('BAI') + 
  geom_line() + geom_point() + scale_colour_manual(values = c("red", "blue")) + 
  theme(panel.grid = element_blank())

# Canar 
cro_caH <- chrono_bai(bai_caH)
cro_caH$site <- 'CA_High'
te <- chrono_bai(bai_caH)
plot.crn(te)
plot(te)
plot(te, add.spline=TRUE, nyrs=30)

@@

cro_ca %>% ggplot(aes(x=year, y=bai_mean/100, colour=site)) + 
  theme_bw() + ylab('BAI') + 
  geom_line() + geom_point() + scale_colour_manual(values = c("red", "blue")) + 
  theme(panel.grid = element_blank())

cro_sites <- rbind(cro_ca, cro_sj)

cro_sites %>% ggplot(aes(x=year, y=bai_mean/100, colour=site)) + 
  theme_bw() + ylab('BAI') + 
  geom_line() + geom_point() + 
  theme(panel.grid = element_blank()) + facet_wrap(~loc, nrow = 2) + 
  scale_colour_manual(values = c('#1b9e77','#d95f02','#7570b3','#e7298a')) + 
  geom_smooth(method= 'loess', span = 0.75, se=FALSE)

 + 
geom_smooth(method= 'loess', span = 0.75, se=FALSE)

  geom_ribbon(aes(x= year, 
                  ymin = loess_fit - 1.96*loess_se,
                  ymax = loess_fit + 1.96*loess_se), na.rm = FALSE, 
              fill = "grey") +
c_sj

c_sj %>% ggplot(aes(x=year, y=bai_mean)) + 
  theme_bw() + 
  geom_ribbon(aes(x= year, 
                  ymin = loess_fit - 1.96*loess_se,
                  ymax = loess_fit + 1.96*loess_se), na.rm = FALSE, 
              fill = "grey") +
  geom_line() + geom_point() + 
  geom_line() + geom_smooth(method= 'loess', span = 0.75, se=FALSE)

bb2 %>% ggplot(aes(x=year, y=bai_mean)) + 
  theme_bw() + 
  geom_ribbon(aes(x= year, 
                  ymin = bai_mean - bai_se,
                  ymax = bai_mean + bai_se), na.rm = FALSE, 
              fill = "grey") +
  geom_line() + geom_point() + 
  geom_smooth(method= 'loess', span = 0.30, se=FALSE)

# IC LOESS

  geom_smooth(method= 'loess', span = 0.30, se=FALSE) + theme_bw() + 
  geom_bar(aes(x=year, stat = (samp.depth*10), colour=treatment))

# cc <- chrono_bai(bai_sj, prefix = "SJ")

chrono_bai <- function(bai_data, prefix){

    if (length(prefix) == 0) {
        prefix.str <- ""
    }
    else {
        prefix.str <- as.character(prefix)[1]
        if (is.na(prefix.str) || Encoding(prefix.str) == "bytes" || 
            nchar(prefix.str) > 3) {
            stop("'prefix' must be a character string with less than 4 characters")
        }
    }
    n_trees <- rowSums(!is.na(bai_data))

    out <- bai_data

    out <- data.frame(samps)
    out
}

@@

```{r}
# centred moved average smooth
# https://cran.r-project.org/web/packages/smooth/vignettes/sma.html

correla_cronos <- function(cronologia, win_vector, crononame){

  cro_object <- cronologia

  # Set bai and years variables 
  bai <- cro_object[,'bai_mean']
  yearss <- cro_object[,'year']

  # object to store 
  out <- c()

  for (i in seq_along(win_vector)){ 
    # moving window size 
    f <- rep(1/i, i)

    # moving average smooth 
    bai_smooth <- stats::filter(bai, f, sides=1)

    # out 
    out_aux <- as.data.frame(cbind(yearss, bai_smooth))

    out_aux$size_wind <- i
    out <- rbind(out, out_aux)
  }
  out$crononame <- crononame 
  out
}

correla_cro_caH <- correla_cronos(cro_caH, win_vector=seq(1,40, by=1), crononame = 'cro_caH')
correla_cro_caL <- correla_cronos(cro_caL, win_vector=seq(1,40, by=1), crononame = 'cro_caL')
correla_cro_sjH <- correla_cronos(cro_sjH, win_vector=seq(1,40, by=1), crononame = 'cro_sjH')
correla_cro_sjL <- correla_cronos(cro_sjL, win_vector=seq(1,40, by=1), crononame = 'cro_sjL')

correla_croSJ <- rbind(correla_cro_sjH, correla_cro_sjL)

# SJ 
out_final <- c()

@@

  aux <- correla_croSJ %>% 
    filter(size_wind == j) %>%
    select(-size_wind) %>% 
    spread(crononame, bai_smooth) %>% 
    as.data.frame()

@@

out_final$site <- 'SJ'

correla_final_sj <- out_final

# CA
correla_croCA <- rbind(correla_cro_caH, correla_cro_caL)
out_final <- c()

@@

  aux <- correla_croCA %>% 
    filter(size_wind == j) %>%
    select(-size_wind) %>% 
    spread(crononame, bai_smooth) %>% 
    as.data.frame()

@@

correla_final_ca <- out_final

correla_finales <- rbind(correla_final_ca, correla_final_sj)
correla_finales %>% 
  ggplot(aes(x=size, y=res.cor, colour=site)) + geom_line()+
  theme_bw() + 
  ylab('Correlation coefficient') + xlab('years(smooth)') + geom_smooth(method = 'loess', se=FALSE)

c11 <- c1[26:nrow(c1),]

cor(c11$cro_sjH, c11$cro_sjL)

ggplot(c1, aes(x=yearss, y=cro_sjH)) + geom_line() + 
  geom_line(aes(x=yearss, y=cro_sjL), colour='blue')

cronologia <- cro_caH
cro_object <- get()
cro_object <- get(cronologia)

plot(cro_caH$year, cro_caH$bai_mean, type='l')
lines(cro_caH$year, y_lag, col="blue")

  y_lag <- filter(y, f20, sides=1)
lines(x, y_lag, col="red")

# average of current sample and 19 previous samples (red)
f20 <- rep(1/20, 20)
f20
#>  [1] 0.05 0.05 0.05 0.05 0.05 0.05 0.05 0.05 0.05 0.05 0.05 0.05 0.05 0.05 0.05 0.05 0.05
#> [18] 0.05 0.05 0.05

@@

  geom_point(aes(x=year, y = samp.depth*100))

cro_ca2 %>% ggplot(aes(x=year, y=bai_mean)) + 
  geom_line(colour='gray') + geom_smooth(method= 'loess', span = 0.80, se=FALSE) + theme_bw() 
+
  geom

plot()

str(cro_ca)

names(cro_ca)

cro_ca <- chron(bai_ca, prefix = "CA", biweight = TRUE)
plot(cro_sjb, add.spline=TRUE, nyrs=30)

cro_sj <- chron(bai_sj, prefix = "SJ", biweight = FALSE)

cc <- cbind(cro_sj, cro_sjb)

su

>>>>

```{r, warning=FALSE, message=FALSE}
library("tidyverse")
library("stringr")
library("dplR")
library("knitr")
# library("detrendeR")
library("pander")
source(paste0(getwd(), '/script/R/bai_piovesan.R'))
source(paste0(getwd(), '/script/R/rw_byTree.R'))
source(paste0(getwd(), '/script/R/chrono_bai.R'))
source(paste0(getwd(), '/script/R/suaviza_cronos.R'))
```

@@

## Compute Chrono 
### San Juan chronologies by site

```{r}
# San Juan 
cro_sjH <- chrono_bai(bai_sjH)
cro_sjH$site <- 'SJ_High'

@@

cro_sj %>% ggplot(aes(x=year, y=bai_mean/100, colour=site)) + 
  theme_bw() + ylab('BAI') + 
  geom_line() + geom_point() + scale_colour_manual(values = c("red", "blue")) + 
  theme(panel.grid = element_blank()) +
  ylab(expression(paste("BAI (", cm^2, year^-1, ")", sep=''))) 
```

### Cañar chronologies by site

```{r}
# Canar 
cro_caH <- chrono_bai(bai_caH)
cro_caH$site <- 'CA_High'

@@

cro_ca %>% ggplot(aes(x=year, y=bai_mean/100, colour=site)) + 
  theme_bw() + ylab('BAI') + 
  geom_line() + geom_point() + scale_colour_manual(values = c("red", "blue")) + 
  theme(panel.grid = element_blank()) +
  ylab(expression(paste("BAI (", cm^2, year^-1, ")", sep=''))) 
```

```{r}
# Combine and plot 
cro_sites <- rbind(cro_ca, cro_sj)

cro_sites %>% ggplot(aes(x=year, y=bai_mean/100, colour=site)) + 
  theme_bw() + ylab('BAI') + 
  geom_line() + geom_point() + 
  theme(panel.grid = element_blank()) + facet_wrap(~loc, nrow = 2) + 
  scale_colour_manual(values = c('#1b9e77','#d95f02','#7570b3','#e7298a')) +
  ylab(expression(paste("BAI (", cm^2, year^-1, ")", sep=''))) 
#  geom_smooth(method= 'loess', span = 0.75, se=FALSE)
```

## Compute similarity between chronos 
Use @Dorado2017 approach.

* Para cada chrono se realiza un suavizado, utilizando diferente tamaño de ventana. 
* Luego calculamos la correlación entre series :red_circle: ask to Isabel and guillermo

```{r}
# centred moved average smooth
suaviza_caH <- suaviza_cronos(cro_caH, win_vector=seq(1,40, by=1), crononame = 'cro_caH')
suaviza_caL <- suaviza_cronos(cro_caL, win_vector=seq(1,40, by=1), crononame = 'cro_caL')
suaviza_sjH <- suaviza_cronos(cro_sjH, win_vector=seq(1,40, by=1), crononame = 'cro_sjH')
suaviza_sjL <- suaviza_cronos(cro_sjL, win_vector=seq(1,40, by=1), crononame = 'cro_sjL')

@@

```{r}
# compute corelations between series 
# SJ 
suaviza_sj <- rbind(suaviza_sjH, suaviza_sjL)

out_final <- c()

@@

  aux <- suaviza_sj  %>% 
    filter(size_wind == j) %>%
    select(-size_wind) %>% 
    spread(crononame, bai_smooth) %>% 
    as.data.frame()

@@

out_final$site <- 'SJ'
correla_sj <- out_final

# CA
suaviza_ca <- rbind(suaviza_caH, suaviza_caL) 
out_final <- c()

@@

  aux <- suaviza_ca %>% 
    filter(size_wind == j) %>%
    select(-size_wind) %>% 
    spread(crononame, bai_smooth) %>% 
    as.data.frame()

@@

correla_ca <- out_final

# Combine datasets and plot coefficient correlation 
correla <- rbind(correla_ca, correla_sj)

correla %>% 
  ggplot(aes(x=size, y=res.cor, colour=site)) + geom_line()+
  theme_bw() + ylim(c(0,1)) +
  ylab('Correlation coefficient') + 
  xlab('Suavizado (centred moving average window size)') + 
  geom_smooth(method = 'loess', se=FALSE) + 
  theme(panel.grid = element_blank())
```

```{r, echo=FALSE, eval=FALSE}

# CODE SNIPPETS 
  # Loess 
  l <- loess(b_aux$bai ~ b_aux$year, span = alpha)
  years_v <- seq(min(b_aux$year), max(b_aux$year), 1)

@@
